---
title       : Canadian Chronic Disease Data Exploration
subtitle    : 
author      : J. Mann 
job         : aspiring data scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, interactive, shiny]              # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The Data

In this project, we choose to explore data published by the Canadian
government on chronic disease. The original data can be found here:
[Chronic Disease Data](http://www.phac-aspc.gc.ca/data-donnees/hpcdp-pspmc/assets/ccdss-scsmc-eng.csv)

An explanation of the variables can be found here: 
[Chronic Disease Variables](http://www.phac-aspc.gc.ca/data-donnees/hpcdp-pspmc/assets/EN_CanadianAggregateDatasets.docx)

The data product itself is found here: [Chronic Disease Explorer](https://crema.shinyapps.io/chronic/)

```{r setOptions, echo=FALSE}
require(googleVis, quietly=TRUE)
require(reshape, quietly=TRUE)
options(gvis.plot.tag="chart")

```

---

## The Visualisation Choices

In this project, I initially worked with the `ggvis` library as it seemed most flexible 
and integrates very nicely with the `dplyr` library. However, one difficulty I 
encountered was that dynamic subsetting was somewhat clumsy. For this reason, 
I switched to the `googleVis` library which provides a lot of functionality “out 
of the box”. There may be some sacrifice in flexibility for this choice.

---  

## Results 

Try adjusting `x` and `y` axis and then hitting the play button on the bottom 

```{r, results='asis', echo=FALSE}
chronic <- read.csv("assets/chronic.csv")
molten.chronic <- melt(chronic, 
            id = c("Disease","Fiscal.Year","Gender","Age.Group"), na.rm = T)
a <- cast(molten.chronic, Disease + Fiscal.Year ~ variable, mean)
M1 <- gvisMotionChart(a, 
                      idvar = 'Disease',
                      xvar="Physician.Visit.with.Disease..Visit.Count_mean",
                      yvar="Mortality.with.Disease_mean", 
                      timevar = 'Fiscal.Year')
print(M1, tag = 'chart')

```

---

## Interesting Observation

One example of the interest of this data product is seen by setting the x-axis 
to `Physician.Visit.with.Disease..Visit.Count_mean` and the y-axis to 
`Mortality.with.Disease_mean`. Three of diseases form an almost perfect straight
line, the exception being `COPD` which reveals a very high mortality rate for a low
number of visits. Perhaps this suggests an area of intervention for our public
health system.

Hopefully this demonstrates some value in this modest data product.
